\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks,colorlinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
\usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.7in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-3pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\hypersetup{%
     colorlinks=true,
     linkcolor=blue,
     filecolor=blue,
     citecolor = black,      
     urlcolor=teal,
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-10pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------

\begin{center}
	\textbf{\Huge \scshape Rohit Mishra} \\ \vspace{1pt}
    \href{tel:+919934086685}{\underline{+919934086685}} $|$
	\href{mailto:iamrht21@gmail.com}{\underline{iamrht21@gmail.com}} $|$ 
	\href{https://linkedin.com/in/rht21}{\underline{LinkedIn}} $|$
	\href{https://github.com/rht-21}{\underline{GitHub}} $|$
	\href{https://rht21.xyz}{\underline{Portfolio}}		    
\end{center}

%-----------PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
\resumeSubHeadingListStart
\resumeItemListStart
    \resumeItem {Results-driven Software Developer with \textbf{1.5 years of professional experience} in designing, developing, and deploying \textbf{scalable and high-performance} web applications.}
    \resumeItem {Proficient in \textbf{JavaScript, TypeScript, and Python}, with expertise in modern front-end frameworks like \textbf{React.js}, \textbf{Next.js}, and \textbf{Tailwind CSS}.}
    \resumeItem {Experienced in \textbf{building user-centric solutions}, optimizing application performance, and implementing \textbf{secure authentication} and \textbf{responsive design} best practices.}
    \resumeItem {Strong collaborator in \textbf{agile environments}, working with cross-functional teams to deliver innovative and maintainable solutions.}
\resumeItemListEnd
\resumeSubHeadingListEnd


%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
	\small{\item{
		\textbf{Languages}{: JavaScript, TypeScript, Python} \\
		\textbf{Databases}{: PostgreSQL, MongoDB} \\
		\textbf{Frameworks \& Libraries}{: Next.js, React.js, Node.js}}}
\end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Nira Tech And Solutions}{Remote}
{Web Developer}{Feb 2024 -- Present}
\resumeItemListStart
    \resumeItem {Develop and maintain user-friendly web applications, improving usability and performance for client-facing platforms.}
    \resumeItem {Build responsive, pixel-perfect UI using React.js and Tailwind CSS, ensuring design consistency and high-quality user experiences.}
    \resumeItem {Collaborate with clients and designers to develop user-focused solutions, meeting project requirements and deadlines.}
    \resumeItem {Integrate APIs and manage data retrieval, enhancing frontend functionality and ensuring seamless communication with backend services.}
\resumeItemListEnd

% \resumeSubheading
% {Addzet Advertising \& Media Pvt. Ltd.}{Bhubaneswar, India}
% {Jr. Web Developer}{Feb 2023 -- Jan 2024}
% \resumeItemListStart
%     \resumeItem {Designed and developed \textbf{responsive websites} for clients, ensuring seamless user experiences across devices.}
%     \resumeItem {Enhanced \textbf{UI/UX designs} by translating wireframes into high-quality code, improving user satisfaction.}
%     \resumeItem {Collaborated with cross-functional teams to align \textbf{frontend designs} with client branding and requirements.}
%     \resumeItem {Optimized \textbf{interactive elements} using modern \textbf{CSS techniques} and \textbf{JavaScript libraries}, increasing engagement.}
%     \resumeItem {Worked on basic \textbf{backend integration} for user authentication and data handling.}
% \resumeItemListEnd

\resumeSubheading
{HighRadius}{Bhubaneswar, India}
{Trainee - Highako}{May 2023 -- Nov 2023}
\resumeItemListStart
    \resumeItem {Refactored and optimized key features, improving processing efficiency by ~20\% through debugging and scalable development practices.}
    \resumeItem {Developed automation tools, including email parsing from EML files and currency formatting (e.g., USD 32), reducing manual effort.}
    \resumeItem {Collaborated in an agile team, resolving issues proactively and meeting tight deadlines.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{\href{https://snipster.rht21.xyz}{Snipster}}{ [ Next.js, MongoDB, Clerk ]}}{Dec 2024}
\resumeItemListStart
    \resumeItem {Developed \textbf{Snipster}, a code snippet management tool to help developers store, organize, and access their code snippets efficiently.}
    \resumeItem {Built a responsive and \textbf{user-friendly interface} with \textbf{Next.js}, providing features like quick search, categorization, and management of snippets.}
    \resumeItem {Integrated \textbf{authentication using Clerk}, ensuring secure login and user management.}
    \resumeItem {Utilized \textbf{MongoDB} for database storage, enabling fast retrieval and secure storage of user snippets.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{\href{https://nexa-vc.vercel.app}{Nexa}}{ [Next.js, Stream, Clerk ]}}{April 2024}
\resumeItemListStart
    \resumeItem {Created an \textbf{intuitive video conferencing app} with features like secure authentication, high-quality video calls, and meeting management.}
    \resumeItem {Implemented \textbf{Clerk} for user authentication, ensuring secure login and access control.}
    \resumeItem {Integrated \textbf{Stream} for high-quality video calls, optimizing the user experience during meetings.}
    \resumeItem {Key features include \textbf{meeting creation}, scheduling, joining, recording, and \textbf{screen sharing} for enhanced collaboration.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Kalinga Institute of Industrial Technology}{Bhubaneshwar, Odissa}
{B.Tech in Information Technology}{2020 -- 2024}
\resumeSubHeadingListEnd

\end{document}
